---
title: "An Exploration on Crypto Currencies"
author: "Emine Doganay, Hale Nur Kaza?esme, Hasan Palaz"
date: "November 18, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The notion of cryptocurrency has entered our lives with the introduction of Bitcoin on Jan 2009. Crypto currencies are decentralized digital currencies, meaning the payment system works without a central repository or administrator. The transactions between users, creation of additional units and verification of transfers are secured by cryptography and logged into the transaction database; blockchain. In most cryptocurrencies, transactions are verified through a process called mining that requires computer processing power to find blocks of transactions and miners are rewarded with newly created crypto coins for their finds. Coins are stored in cryptocurrency wallets, which are essentially a collection of cryptographic keys. Yes, it is hard to digest the mechanics behind cryptocurrencies.  
  
With the uncontrollable climb of Bitcoin and all these buzzwords flying around, cryptocurrencies became a hype. Part of the hype is created by the mystery caused by the enigmatic nature of cryptocurrencies and the obscurity of the workings of blockchain. The suspicion surrounding the future of cryptocurrencies were not only founded on the fear of the unknown but also on the fact that they can be lost forever from their markets due malware or data loss or even an accident as in a recent incident with an Etherium wallet that caused approximately $280m worth of Ether to be frozen.  
  
All this said, our aim is to understand and relate cryptocurrencies to shed some light onto this conundrum. We will try to understand the correlation between crytocurrencies, correlation with gold and how google trends are related to Bitcoin price.  


```{r, echo=FALSE, cache=TRUE, message=FALSE}
# An Exploration on cryptocurrencies

# Clean R environment, Remove everything from environment
rm(list=ls(all=TRUE))

# Install and load required libraries
# rvest: a package to read web data, easy web scraping with R; https://blog.rstudio.com/2014/11/24/rvest-easy-web-scraping-with-r/
if(!require(rvest)) install.packages("rvest")
library(rvest)
# plotrix: Various Plotting Functions;Lots of plots, various labeling, axis and color scaling functions.
if(!require(plotrix)) install.packages("plotrix")
library(plotrix)
# dplyr package is for data manipulation
if(!require(dplyr)) install.packages("dplyr")
library(dplyr)
# Treemaps display hierarchical data as a set of nested rectangles.
if(!require(treemap)) install.packages("treemap")
library(treemap)
if(!require(ggplot2)) install.packages("ggplot2")
library(ggplot2)
if(!require(corrplot)) install.packages("corrplot")
library(corrplot)
if(!require(plotly)) install.packages("plotly")
library(plotly)
if(!require(quantmod)) install.packages("quantmod")
library(quantmod)
```

We read the data directly from coinmarketcap.com using package rvest. The data looks like:  

```{r, echo=FALSE, cache=TRUE, message=FALSE}

# Define URL where retrieve cryptocurrencies datas, the URL is coinmarketcap.com
url_cryptocurrencies <- "https://coinmarketcap.com/currencies/views/all/"

# Read the price table
# The data, CryptoCurrency Market Capitalizations (CMC) price chart, is "read" from their website to df_cryptocurrencies dataframe
url_cryptocurrencies %>% 
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table() %>%
  as.data.frame() -> "df_cryptocurrencies" # save table to variable df_cryptocurrencies
# Let's see what we have as df_cryptocurrencies
head(df_cryptocurrencies, 4)
# View(df_cryptocurrencies)
```
We can see that the data contains a few unwanted characters such as new line, \n, $,*, spaces, %. In order to conduct analysis, we need to remove these characters.

An alternative way to retrive data is to use the JSON API at api.coinmarketcap.com which provides clean data. The data from the JSON API looks like:  

```{r, cache=TRUE, echo=FALSE}
# Alternate (second) way to retreive datas (price infos of cryto currencies) by using JSON API from api.coinmarketcap.com
# The JSON API provide clean data
if(!require(jsonlite)) install.packages("jsonlite")
library(jsonlite)

allCurrencies_cmc <- as.data.frame(fromJSON("https://api.coinmarketcap.com/v1/ticker/"))
allCurrencies_cmc$rank <- NULL
allCurrencies_cmc[,c(-1,-2,-3)] <- lapply(allCurrencies_cmc[,c(-1,-2,-3)], as.numeric)
# Let's view dataframe, allCurrencies_cmc
head(allCurrencies_cmc, 4)

# The JSON API provides more cleaner data than RVEST, 
# but we apply cleaning steps to dirty dataframe which was retreived by RVEST 
```
which is much cleaner aside from NA's. But to demonstrate what we have learned in this class we chose to work with the data collected with rvest package and cleaned it.
```{r, echo=TRUE, cache=TRUE}
# Cleaning the data
# Before cleaning, "\n" in the name strings should be replaced with "-" in df_cryptocurrencies$Name column
df_cryptocurrencies$Name <- lapply(df_cryptocurrencies$Name, gsub, pattern = "\n", replacement = "-")

# In order to conduct analysis, we need to remove the unwanted characters such as \n, $,*, spaces, %.
df_cryptocurrencies[] <- lapply(df_cryptocurrencies, gsub, pattern = "\\\n|\\s|[%*$,?]", replacement = "")

# remove the first column X. (coins' ranking of coinmarketcap web site) 
df_cryptocurrencies$X. <- NULL

# Update the column names short, lowercase and meaningful
names(df_cryptocurrencies) <- c("name", "symbol", "marketcap", "price", "supply", "volume", "change_1h", "change_24h", "change_7d")

# Let's see how our data frame, df_cryptocurrencies looks after cleaning process
head(df_cryptocurrencies)
```
For mathematical analysis variable types should be numeric.
```{r, cache=TRUE}
# Check type of marketcap
typeof(df_cryptocurrencies$marketcap)
```
However some are not. So we transform the type of variables except name and symbol to numeric and assign into a new data frame. And after transformation data type of marketcap becomes:
```{r, cache=TRUE, echo=FALSE, warning=FALSE}
num_df_cryptocurrencies <- lapply(df_cryptocurrencies[-c(1:2)], as.numeric) %>% as.data.frame()
df_allcryptocurrencies <- cbind(df_cryptocurrencies$name, df_cryptocurrencies$symbol, num_df_cryptocurrencies)
names(df_allcryptocurrencies) <- c("name", "symbol", "marketcap", "price", "supply", "volume", "change_1h", "change_24h", "change_7d")
# Check type of marketcap, be sure that it is numeric
typeof(df_allcryptocurrencies$marketcap)
```
Let's see how our data frame looks like now:
```{r, cache=TRUE, echo=FALSE}
head(df_allcryptocurrencies, 4)
#dimensions
dim(df_allcryptocurrencies)
```
and how many coins are there in the market?
```{r, cache=TRUE, echo=FALSE}
nrow(df_allcryptocurrencies)
```
When you consider there are only 180 recognized currencies in the world this is a huge number. However not all of them are big players. Let's draw the market share of all crypto currencies as a treemap to get a better understanding:
```{r, cache=TRUE, echo=FALSE}
df_allcryptocurrencies$formatted_market_cap <-  paste0(df_allcryptocurrencies$name,'\n','$',format(df_allcryptocurrencies$marketcap,big.mark = ',',scientific = F, trim = T))
treemap(df_allcryptocurrencies, index = 'formatted_market_cap', vSize = 'marketcap', title = 'Cryptocurrency Market Capitalizations', fontsize.labels=c(12, 8), palette='RdYlGn')
```
  
Normal currencies are dependable because they have a relatively stable standing against each other and their market only gets effected from big political or economical events. However with a decentralized non-physical currency it all works differently. With no mechanism to act on a financial policy to regulate sudden price changes, price of the crypto-currencies are literally defined in the market.  
Let's see how big these changes can be by exploring the evolution of the market in 1 hour, 24 hours and 7 days for all crypto currencies.  
Summary of statistics and standard deviation of market change in 1 hour are as follows:
```{r, cache=TRUE}
summary(df_allcryptocurrencies$change_1h)
sd(df_allcryptocurrencies$change_1h, na.rm=TRUE)
```
Summary of statistics and standard deviation of market change in 24 hours are as follows:
```{r, cache=TRUE}
summary(df_allcryptocurrencies$change_24h)
sd(df_allcryptocurrencies$change_24h, na.rm=TRUE)
```
Summary of statistics and standard deviation of market change in 7 days are as follows:
```{r, cache=TRUE}
summary(df_allcryptocurrencies$change_7d)
sd(df_allcryptocurrencies$change_7d, na.rm=TRUE)
```

```{r, cache=TRUE, echo=FALSE}
boxplot(df_allcryptocurrencies$change_7d, horizontal=TRUE, col= c("red"), main="Box plot of Evolution of Currencies in 7 days")
hist(df_allcryptocurrencies$change_7d, col="purple",main="Histogram of Evolution of Currencies in 7 days",xlab="An Evolution of Currencies in 7 days")
```
  
However these price changes don't mean much without the context. Surely an \$100 increase of Bitcoin (which is valued about \$8000 at the time of this writing) is not the same an \$100 increase of Ethereum (which is valued about \$300 at the time of this writing). Let's find all the cryptocurrencies whose value has more than doubled in 7 days:
```{r, cache=TRUE, echo=FALSE}
df_allcryptocurrencies_double_in7d <- df_allcryptocurrencies[df_allcryptocurrencies$change_7d > 100,]
df_allcryptocurrencies_double_in7d <- df_allcryptocurrencies_double_in7d[complete.cases(df_allcryptocurrencies_double_in7d),]
df_allcryptocurrencies_double_in7d$name
```
  
and let's find all the cryptocurrencies which lost more than 25% of its value in 7 days:
```{r, cache=TRUE, echo=FALSE}
df_allcryptocurrencies_reduced_in7d <- df_allcryptocurrencies[df_allcryptocurrencies$change_7d < -25,]
df_allcryptocurrencies_reduced_in7d <- df_allcryptocurrencies_reduced_in7d[complete.cases(df_allcryptocurrencies_reduced_in7d),]
df_allcryptocurrencies_reduced_in7d$name
```
  
By the tree chart above we know that Bitcoin is the dominant player in the market.  
The total market capitalization currently is:  
```{r, cache=TRUE, echo=FALSE}
total_coin_market_cap <-sum(df_allcryptocurrencies$marketcap, na.rm=TRUE)
Bitcoin_Dominance <- df_allcryptocurrencies$marketcap[1]/total_coin_market_cap
# Format total_coin_market_cap and BitcoinDominance for easy understanding and presenting very well
total_coin_market_cap_formatted <-  paste0('$',format(total_coin_market_cap,big.mark = ',',scientific = F, trim = T))
Bitcoin_Dominance_formatted <-  paste0(format(Bitcoin_Dominance, big.mark = ',',scientific = F, trim = T),'%')
total_coin_market_cap_formatted
```
  
and Bitcoin's share is:
```{r, cache=TRUE, echo=FALSE}
Bitcoin_Dominance_formatted
```
Even though Bitcoin is sharing the market with more and more crypto currencies each day, it remains the biggest player.
  
Let's focus on top 10 currrencies by market cap.
```{r, cache=TRUE, echo=FALSE}
# Total coin market cap, aggregate
total_coin_market_cap <-sum(df_allcryptocurrencies$marketcap, na.rm=TRUE)
top_10_market_cap <- arrange(.data = df_allcryptocurrencies, desc(marketcap))[1:10, ]
# Add a column named <marketcap_percent> which percentage of a cryptocurrency market share
top_10_market_cap$marketcap_percent <- top_10_market_cap$marketcap/total_coin_market_cap
# Display first to 10 crypto currencies by market cap 
head(top_10_market_cap, 10)
```
Total market share of the top 10 coins is:
```{r, cache=TRUE, echo=FALSE}
market_share_top_10 <- (sum(top_10_market_cap$marketcap)/total_coin_market_cap)*100
market_share_top_10_formatted <-  paste0(format(market_share_top_10, big.mark = ',',scientific = F, trim = T),'%')
market_share_top_10_formatted
# Market Cap of top 10 currencies as 3D pie chart
# Create labels for pie chart
lbls <- paste0(top_10_market_cap$name, " : ", sprintf("%.2f", top_10_market_cap$marketcap_percent*100), "%")
pie3D(top_10_market_cap$marketcap_percent, labels = lbls,
      explode=0.5, main="Top 10 Cryptocurrencies Market Share")
```

Since we are focusing on the top currencies we gather historical data from CoinMarketCap web site as the top curriencies go way back than some other small currencies. HTML data is converted into a dataframe because there is no API to get the historic data of cryptocurrencies. We will study the daily evolution of top 5 cryptocurrencies: 
```{r, cache=TRUE, echo=FALSE}
top_5_market_cap <- arrange(.data = df_allcryptocurrencies, desc(marketcap))[1:5, ]
# Add a column named <marketcap_percent> which percentage of a cryptocurrency market share
top_5_market_cap$marketcap_percent <- top_5_market_cap$marketcap/total_coin_market_cap
# Display first to 10 crypto currencies by market cap 
subset(top_5_market_cap, select = c(name, symbol))
```
We import the historical data for these currencies.
```{r, cache=TRUE, echo=FALSE, warning=FALSE}
Months <- data.frame('01', '02', '03', '04', '05', '06', '07', '08', '09', '10', '11', '12', stringsAsFactors = F)
colnames(Months) <- c('Jan', 'Feb', 'Mar', 'Apr', 'May', 'Jun', 'Jul', 'Aug', 'Sep', 'Oct', 'Nov', 'Dec')

convertTime <- function(string) {
  return(as.Date(paste(substr(string, 6, 9), "-", as.character(Months[substr(string, 1, 3)]), "-", substr(string, 4, 5), sep = "")))
}

getHistoric <- function(coin = 'bitcoin', start = '2013-04-28', end = Sys.Date()) {
  start = strsplit(as.character(start), split='-')[[1]]
  start = paste(start[1], start[2], start[3], sep = "")
  end = strsplit(as.character(end), split='-')[[1]]
  end = paste(end[1], end[2], end[3], sep = "")
  url <- paste("https://coinmarketcap.com/currencies/", coin, 
               "/historical-data/?start=", start, "&end=", end, sep="")
  data <- as.data.frame(html_table(html_nodes(css = "table", x = read_html(url))))
  data[] <- lapply(data, gsub, pattern = "\\\n|\\s|[%*$,?]", replacement = "")
  data$X. <- NULL
  data[-1] <- sapply(data[-1], as.numeric)
  data$Date <- convertTime(data$Date)
  data <- addPercentage(data)
  return(data)
}

addPercentage <- function(data) {
  data$Percentage <- c(0,(data$Close[2:nrow(data)] - data$Close[1:(nrow(data)-1)]) / data$Close[2:nrow(data)])
  return(data)
}
```
Bitcoin
```{r, cache=TRUE, echo=FALSE, warning=FALSE}
# Import Bitcoin historical price datas
df_bitcoin <- getHistoric(coin = 'bitcoin', start = '2013-04-28', end = Sys.Date())
# Let's check everything is OK
summary(df_bitcoin)
# Save Bitcoin historical price to file named bitcoin_historical_price.csv (in the working directory)
write.csv(df_bitcoin, file = "bitcoin_historical_price.csv")
```
Ethereum
```{r, cache=TRUE, echo=FALSE, warning=FALSE}
# Import Ethereum historical price datas
df_ethereum <- getHistoric(coin = 'ethereum', start = '2013-04-28', end = Sys.Date())
# Let's check everything is OK
summary(df_ethereum)
# Save Ethereum historical price to file named ethereum_historical_price.csv (in the working directory)
write.csv(df_ethereum, file = "ethereum_historical_price.csv")
```
BitcoinCash
```{r, cache=TRUE, echo=FALSE, warning=FALSE}
# Import BitcoinCash historical price datas
df_bitcoincash <- getHistoric(coin = 'bitcoin-cash', start = '2013-04-28', end = Sys.Date())
# Let's check everything is OK
summary(df_bitcoincash)
# Save BitcoinCash historical price to file named bitcoincash_historical_price.csv (in the working directory)
write.csv(df_bitcoincash, file = "bitcoincash_historical_price.csv")
```
Ripple
```{r, cache=TRUE, echo=FALSE, warning=FALSE}
# Import Ripple historical price datas
df_ripple <- getHistoric(coin = 'ripple', start = '2013-04-28', end = Sys.Date())
# Let's check everything is OK
summary(df_ripple)
# Save Ripple historical price to file named ripple_historical_price.csv (in the working directory)
write.csv(df_ripple, file = "ripple_historical_price.csv")
```
Litecoin
```{r, cache=TRUE, echo=FALSE, warning=FALSE}
#Import Litecoin historical price datas
df_litecoin <- getHistoric(coin = 'litecoin', start = '2013-04-28', end = Sys.Date())
# Let's check everything is OK
summary(df_litecoin)
# Save Litecoin historical price to file named litecoin_historical_price.csv (in the working directory)
write.csv(df_litecoin, file = "litecoin_historical_price.csv")
```


```{r, cache=TRUE, echo=FALSE}
#Prepare date format of top 5 crypto currencies
df_bitcoin$Date <- as.Date(df_bitcoin$Date)
df_ethereum$Date <- as.Date(df_ethereum$Date)
df_bitcoincash$Date <- as.Date(df_bitcoincash$Date)
df_ripple$Date <- as.Date(df_ripple$Date)
df_litecoin$Date <- as.Date(df_litecoin$Date)

```

If we plot the high prices of these 5 currencies together we get.
```{r, cache=TRUE, echo=FALSE, warning=FALSE}
plot(df_bitcoin$Date,df_bitcoin$High, type = 'line', col="blue", main = 'Curriencies High Price', xlab ='Date', ylab = 'High Price')
lines(df_ethereum$Date,df_ethereum$High, col="red")
lines(df_bitcoincash$Date,df_bitcoincash$High, col='green')
lines(df_ripple$Date,df_ripple$High, col="orange")
lines(df_litecoin$Date,df_litecoin$High, col='black')
legend("topleft", legend=c("bitcoin", "Ethereum", "bitcoincash", "ripple", "litecoin"), 
       col=c("blue", "red", "green", "orange","black"), lty=1:2, bty ="n" , cex=0.5)
```

Our motivation to work with cryptocurriencies actually comes from this; look at that steep increase in a year. But when you look closely it's not a smooth increase. With a candlestick plot we can see that the price is always alternating between increasing and decreasing.

```{r, cache=TRUE, echo=FALSE, warning=FALSE}
p <- df_bitcoin %>%
  plot_ly(x = df_bitcoin$Date, type="candlestick",
          open = df_bitcoin$Open, close = df_bitcoin$Close,
          high = df_bitcoin$High, low = df_bitcoin$Low) %>%
  add_lines(y = df_bitcoin$Open, line = list(color = 'black', width = 0.75)) %>%
  layout(title= "Bitcoin Candlestick Chart", showlegend = TRUE)
p
```

Focusing on only the last 30 days.
```{r, cache=TRUE, echo=FALSE}
i <- list(line = list(color = '#FFD700'))
d <- list(line = list(color = '#0000ff'))
df_bitcoin_Last30 <- head(df_bitcoin, n = 30)
p <- df_bitcoin_Last30 %>%
  plot_ly(x = df_bitcoin_Last30$Date, type="candlestick",
          open = df_bitcoin_Last30$Open, close = df_bitcoin_Last30$Close,
          high = df_bitcoin_Last30$High, low = df_bitcoin_Last30$Low,
          increasing = i, decreasing = d) %>%
  layout(title = "Candlestick Chart For Bitcoin: Last 30 Days")
p
```

This means between the day we decided on this project and today we could've increased our money by 33% ! That is a huge amount. Let's examine the percentage of price changes for Bitcoin to see if this is normal.

```{r, cache=TRUE}
summary(df_bitcoin$Percentage)
sd(df_bitcoin$Percentage)
```
Bitcoin is highly volatile; it has gained up to 23% or lost up to 43% in only one day.
```{r, cache=TRUE, echo=FALSE}
# Plot bitcoin price versus time
p_01 <- ggplot(data = df_bitcoin)
p_01 + labs(title = "History of Bitcoin Price") + labs(x = "Date") + labs(y = "Price in USD") + geom_line(aes(x = Date, y = Close)) 
```

Let's examine the percentage of price changes for Ethereum to see if a similer phenomenon occurs.
```{r, cache=TRUE}
summary(df_ethereum$Percentage)
sd(df_ethereum$Percentage)
```

Ethereum is also extremely volatile for a currency; it has gained up to 72% or lost up to 51% in only one day.
```{r, cache=TRUE, echo=FALSE}
# Plot Ethereum price versus time
p <- ggplot(data = df_ethereum)
p + geom_line(aes(x = Date, y = Close)) + labs(x = "Date") + labs(y = "Price in USD") + labs(title = "History of Ethereum Price")
```

Correlation between cryptocurrencies' closing prices gives us an idea if they behave similarly to normal currencies or if people treat them basically being the same since they are not affiliated with anything but code chunks and blockchains.

```{r, cache=TRUE, echo=FALSE}
correlation <- cor(cbind(Bitcoin = df_bitcoin[df_bitcoin$Date > as.Date('2017-07-23'),]$Close, Ethereum = df_ethereum[df_ethereum$Date > as.Date('2017-07-23'),]$Close, Ripple = df_ripple[df_ripple$Date > as.Date('2017-07-23'),]$Close, Litecoin = df_litecoin[df_litecoin$Date > as.Date('2017-07-23'),]$Close, Bitcoincash = df_bitcoincash[df_bitcoincash$Date > as.Date('2017-07-23'),]$Close))
corrplot(correlation)
#correlation
```

We can see that, at least the top five cryptocurrencies are correlated. This means that a negative news about one might affect the others negatively even if not at the same magnitude. 

Wait a second! Are we jumping to conclusions here? Remember, these all sail at different price levels so we need some sort of normalization. Currently we trying to correlate a data like this:

```{r, cache=TRUE, echo=FALSE, warning=FALSE}
#In here; open and close price graphs for 5 top curriencies is given in the same plot.
plot(df_bitcoin$Date,(df_bitcoin$Close-df_bitcoin$Open), type = 'line', col="blue", main = 'Daily Differences between Opening and Closing Price', xlab ='Date', ylab = 'Differences')
lines(df_ethereum$Date,(df_ethereum$Close-df_ethereum$Open), col="red")
lines(df_bitcoincash$Date,(df_bitcoincash$Close-df_bitcoincash$Open), col='green')
lines(df_ripple$Date,(df_ripple$Close-df_ripple$Open), col="orange")
lines(df_litecoin$Date,(df_litecoin$Close-df_litecoin$Open), col='black')
legend("topleft", legend=c("bitcoin", "Ethereum", "bitcoincash", "ripple", "litecoin"), 
       col=c("blue", "red", "green", "orange","black"), lty=1:5, bty ="n" , cex=0.6)
```

You can't even see Ripple and Litecoin in the graph.
But after normalizing by turning them into percentage changes the data we are trying to correlate becomes like this:

```{r, cache=TRUE, echo=FALSE, warning=FALSE}
plot(df_bitcoin$Date,df_bitcoin$Percentage, type = 'line', col="blue", main = 'Percentage of Closing Price', xlab ='Date', ylab = 'Differences')
lines(df_ethereum$Date,df_ethereum$Percentage, col="red")
lines(df_bitcoincash$Date,df_bitcoincash$Percentage, col='green')
lines(df_ripple$Date,df_ripple$Percentage, col="orange")
lines(df_litecoin$Date,df_litecoin$Percentage, col='black')
legend("topleft", legend=c("bitcoin", "Ethereum", "bitcoincash", "ripple", "litecoin"), 
       col=c("blue", "red", "green", "orange","black"), lty=1:2, bty ="n" , cex=0.5)
```


Let's look at the correlation between the percentage changes:

```{r, cache=TRUE, echo=FALSE}
# Correlation of volatility between cryptocurrencies
correlation <- cor(cbind(Bitcoin = df_bitcoin[df_bitcoin$Date > as.Date('2017-07-23'),]$Percentage, Ethereum = df_ethereum[df_ethereum$Date > as.Date('2017-07-23'),]$Percentage, Ripple = df_ripple[df_ripple$Date > as.Date('2017-07-23'),]$Percentage, Litecoin = df_litecoin[df_litecoin$Date > as.Date('2017-07-23'),]$Percentage, Bitcoincash = df_bitcoincash[df_bitcoincash$Date > as.Date('2017-07-23'),]$Percentage))
corrplot(correlation)
```

The correlations have weakened a little bit and BitcoinCash seems to be acting independently. So, good news! You might still bet on some crypto currencies while shorting others and make money on both exchanges! 
Obligatory Warning: The market is highly volatile so it can be too risky.

Since Bitcoin was first to market, has limited supply and unregulated a natural question to ask is "how similar it is to gold"? Correlation with the well known asset and the gold of the digital world is:
```{r, cache=TRUE, echo=FALSE}
correlation <- function(series1, series2, k = 0) {
  len = length(series1)
  return(cor(cbind(series1[1:(len-k)], series2[(1+k):len]), use = 'na.or.complete')[1,2])
}
# The daily prices of gold on Quandl are downloaded as CSV format, gold_daily.csv
Gold_Data <- read.csv('gold_daily.csv', header = T, stringsAsFactors = F)
df_Gold <- data.frame(Date = as.Date(Gold_Data$Date), Close = Gold_Data$Value)
correlation(df_bitcoin$Close, df_Gold[is.element(df_Gold$Date,df_bitcoin$Date),]$Close)
```

It can be seen that the correlation is nothing of importance. Bitcoin is only a tiny fraction of gold in terms of market capitalization and gold's physical vs Bitcoin's digital makes them two separate markets even though you can mine Bitcoins, too.

We have talked about the speculative aspect of crypto currencies, let's see if our intuition was correct on this one. In here, we try to define the correlation between bitcoin and google search by comparing historical price datas to Google search trend of Bitcoin.
```{r, cache=TRUE, echo=FALSE}
df_GoogleSearch <- read.csv('multiTimeline.csv', header = F, stringsAsFactors = F)[c(-1,-2),]
colnames(df_GoogleSearch) <- c('Date', 'Volume')
df_GoogleSearch$Date <- as.Date(df_GoogleSearch$Date)
df_GoogleSearch$Volume <- as.numeric(df_GoogleSearch$Volume)
row.names(df_GoogleSearch) <- NULL
df_GoogleSearch <- df_GoogleSearch[nrow(df_GoogleSearch):1,]
correlation(df_GoogleSearch$Volume, df_bitcoin[is.element(df_bitcoin$Date, df_GoogleSearch$Date),]$Close)
```
Yes, they are extremely correlated! This could mean that the price of crypto currencies can be affected from negative or positive publicity and/or vice versa; a huge change in prices might spark interest and sequentially people might be searching for more information on them.



Linear regression analysis between bitcoin high price and Ethereum high price for last 30 days.
```{r, cache=TRUE, echo=FALSE, warning=FALSE}
df_bitcoin_Last30 <- head(df_bitcoin, n = 30)
df_ethereum_Last30<-head(df_bitcoin, n=30)
df_bitcoin_RegModel3 <- lm(formula = df_bitcoin_Last30$High ~ df_ethereum_Last30$High, data=c(df_bitcoin_Last30,df_ethereum_Last30)) # regression formula
summary(df_bitcoin_RegModel3) # show regression coefficients table
plot(df_bitcoin_Last30$High, df_ethereum_Last30$High)
abline(df_bitcoin_RegModel3,col ='red')
```

As it is seen in the figure; there is linear relationships between Ethereum and Bitcoin high prices. 
Linear Regression between bitcoin closing price and high price gives us

```{r,cache=TRUE, echo=FALSE}
df_bitcoin_RegModel <- lm(formula = Close ~ High, data=df_bitcoin) # regression formula
summary(df_bitcoin_RegModel) # show regression coefficients table
plot(df_bitcoin$Close, df_bitcoin$High)
abline(df_bitcoin_RegModel,col ='red')

# Summarize and print the results
df_bitcoin_RegModel2 <- lm(Volume ~ Market.Cap + High + Percentage, data = df_bitcoin)
summary(df_bitcoin_RegModel2) # show regression coefficients table
plot(df_bitcoin_RegModel2, which= 1)

```


These analyses helped us to understand cryptocurrencies a little better and lifts the veil of mystery around them a bit. Of course every mind asks different questions. Our minds wandered to the question of whether we can use machine learning techniques to make money of off this. Hence we applied 4 methods on python to understand the data better and see how they performed.

Summary of results; we get 58% accuracy on KNN and SVM for Bitcoin price predictions trained on past 30 days of prices. However this result is not that great considering the upward trajectory of Bitcoin. The best predictor predicted if it will go up with 55% accuracy and it will go down with 53% accuracy. That means we won't be rich tomorrow. But we didn't lose hope, we will try again.